%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Preface}

The work presented in \autoref{ch:Goormaghtigh} is joint work with Dr. M. Bennett and Dr. D. Kreso and has been submitted for publication \cite{BeGhKr}. I was responsible for modifying and specializing the Thue-Mahler algorithm to resolve the remaining cases, $0 \leq x \leq 720$, for $n = 5$. I implemented the resulting algorithm in Magma and performed the tests on each remaining case, as well as wrote \autoref{TM}. The remainder of the work submitted for publication was originally drafted by M. Bennett and D. Kreso. 

\autoref{ch:EllipticCurves} is work completed in collaboration with Dr. M. Bennett and Dr. A. Rechnitzer. A version of this chapter has been published and appears in M. A. Bennett, A. Gherga and A. Rechnitzer, \emph{Computing elliptic curves over $\mathbb{Q}$}, Math. Comp. 88 (2019), no. 317, 1341-1390. In this work, I modified and implemented all of the code needed to resolve the reducible and irreducible forms. Furthermore, I was responsible for running this code to generate all of the solutions and resulting elliptic curves to the forms in the section ``Examples''. I drafted the majority of this section, while the remainder of the paper was originally drafted by M. Bennett and A. Rechnitzer.

\autoref{ch:AlgorithmsForTM} and \autoref{ch:EfficientTMSolver} is part of an ongoing collaborative project, currently in preparation \cite{GhKaMaSi} with Dr. B. Matshke, Dr. R. von K\"anel, and Dr. S. Siksek. The ideas presented in \autoref{sec:PIRL} and \autoref{subsec:FactorizationTMwithoutOK} are attributed to S. Siksek. The work in \autoref{ch:EfficientTMSolver} is joint work with R. von K\"anel, to whom the new ideas are attributed. Here, I helped to develop the theory and details behind these ideas, as well as implemented and tested the algorithm presented in both chapters.


